NLTK: The Natural Language Toolkit

### 2002-05-06 technical/acl2002/acl02.tex
first commit of acl02.tex
svn/trunk@547
removed submission-specific macros
svn/trunk@549

%
% Submission for ``Effective Tools And Methodologies For Teaching
% Natural Language Processing And Computational Linguistics'' workshop
% at ACL 2002
%
% Authors: Edward Loper and Steven Bird
% 
% $Id$
%
\documentclass[11pt]{article}
\usepackage{acl02sub,url,alltt,epsfig}
\title{NLTK: The Natural Language Toolkit}
\author{
Edward Loper and Steven Bird\\
Department of Computer and Information Science and Linguistic Data Consortium\\
University of Pennsylvania, Philadelphia, PA 19104-6389, USA
}
\summary{%
NLTK, the Natural Language Toolkit, is a suite of program modules,
tutorials and problem sets, providing ready-to-use computational
linguistics courseware.  NLTK covers symbolic and statistical natural
language processing, and is interfaced to annotated corpora.  Students
augment and replace existing components, learning structured
programming by example, and manipulating sophisticated models from the
outset.}

\paperid{Pxxxx}
\keywords{teaching, courseware, Python, corpora}
\contact{Edward Loper}
\conference{this paper has not been submitted to any other
conferences}
% In the submission example, they had \date{}; but \date{\today} is
% helpful when printing draft copies, to keep track of versions.
%\date{\today}
\date{}

% Note: the maximum paper length is 6 pages.

@@

\begin{document}
\makeidpage
\maketitle

% ===================== Abstract =====================
% [EL] I think that this abstract should be left out, or shortened and
% merged with the \summary.  The text in the 1st paragraph of the intro
% seems much more direct and relevant to our project than the 1st
% paragraph of this abstract (in particular, the 1st sentence seems like
% a strange way to start). :) I don't think that the second paragraph
% needs to be included in the abstract -- it's not a central point of
% our paper; and the third paragraph is almost identical to the \summary
% (but not quite).  For now, I'm just commenting out the abstract.

%\begin{abstract}
%Students in computational linguistics courses must often learn a new
%programming language.  In some cases, such as when courses are offered
%in linguistics departments, the students may be learning to program
%for the very time.  In order to do interesting projects, it is usually
%necessary for students to do many low-level ``housekeeping'' tasks.
%At the same time, teachers of computational linguistics courses
%sometimes feel that they spend too much time teaching students to
%program, and not enough time teaching the subject itself.  They may
%even avoid programming assignments altogether.  However, we believe
%that it is crucial for a first computational linguistics course to
%include a strong practical component, in which students develop real
%programs to solve real problems with real data.
%
%Python is a new object-oriented scripting language which runs on all
%platforms.  Python has been praised as ``executable pseudocode,'' since
%programs are so easy to write.  Recently, we have been developing
%NLTK, an open-source Natural Language Toolkit written in Python.
%In this presentation, we will motivate, describe and demonstrate NLTK.
%
%NLTK, the Natural Language Toolkit, is a suite of program modules,
%tutorials and problem sets.  NLTK covers symbolic and statistical
%natural language processing, and is interfaced to annotated corpora.
%Students augment and replace existing NLTK components, learning
%structured programming by example, and manipulating sophisticated
%models from the outset.  Along with extensive documentation and
%problem sets, NLTK provides self-contained, ready-to-use CL
%courseware.
%\end{abstract}

@@

\bibliographystyle{acl}
\bibliography{submission}

>>>>

%
% Submission for ``Effective Tools And Methodologies For Teaching
% Natural Language Processing And Computational Linguistics'' workshop
% at ACL 2002
%
% Authors: Edward Loper and Steven Bird
% 
% $Id$
%
\documentclass[11pt]{article}
\usepackage{acl2002,url,alltt,epsfig}
\title{NLTK: The Natural Language Toolkit}
\author{
Edward Loper and Steven Bird\\
Department of Computer and Information Science and Linguistic Data Consortium\\
University of Pennsylvania, Philadelphia, PA 19104-6389, USA
}
\date{}

@@

\begin{document}
\maketitle

\begin{abstract}
NLTK, the Natural Language Toolkit, is a suite of program modules,
tutorials and problem sets, providing ready-to-use computational
linguistics courseware.  NLTK covers symbolic and statistical natural
language processing, and is interfaced to annotated corpora.  Students
augment and replace existing components, learning structured
programming by example, and manipulating sophisticated models from the
outset.
\end{abstract}

@@

\bibliographystyle{acl}
\bibliography{nltk}
